|

### 2025-05-06 doc/paper.qmd
Updated list of abbreviations

# List of Abbreviations {-}
\setlength{\parindent}{0em}
**BHR**: Buy-and-Hold Returns   
**CRSP**: Center for Research in Security Prices  
**DS**: Datastream  
**IDE**: Integrated Development Environment  
**TREAT**: TRR 266 Template for Reproducible Empirical Accounting Research  
**WRDS**: Wharton Research Data Services  
**WSCP**: Worldscope

>>>>

# List of Abbreviations {-}
\setlength{\parindent}{0em}
\begin{tabular}{@{}ll}
\textbf{BHR}   & Buy-and-Hold Returns \\
\textbf{CRSP}  & Center for Research in Security Prices \\
\textbf{DS}    & Datastream \\
\textbf{IDE}   & Integrated Development Environment \\
\textbf{TREAT} & TRR 266 Template for Reproducible Empirical Accounting Research \\
\textbf{WRDS}  & Wharton Research Data Services \\
\textbf{WSCP}  & Worldscope \\
\end{tabular}
